A few stickleback suffice to transport adaptive alleles to new lakes

### 2018-12-12 Stickleback_Paper.tex
gramm

In this paper, we have described a realistic simulation model to observe the effects of selection of genetic variation (SGV) across a wide range of gene flow rates.
we have shown that historical introgression, at our given parameter sets, is able to reproduce rapid and parallel adaptation similar to what we've seen in real populations such as Middleton island. 
Selection is able to rebuild the freshwater haplotype at a rapid pace (in tens of generations) from marine populations as a medium between all freshwater populations. 
Almost all rates of migration were helpful in the efficiency of the population to locally adapt except for the highest at which migration load limited the ability of the populations to reach the local optimum.

While our findings prove useful to the understanding of stickleback, they are not autonomous to this species. 
Now, we will discuss the broader implications of our findings on the more general framework of similar systems, we also explore what other questions remain. 
Small patches of similar selective pressures can be found in many places such as high altitudes, underwater volcanic vents, or post forest fire environments. 
%We are still finding new subspecies, that seem to have adapted to extreme environments presented in small patches connected to larger spanning biospheres where the ancestral species naturally inhabits.
Recently, (Cite Nelson Ferretti et al), discovered seven new species of Hapalotremus (Theraphosinae), living at the extremely high altitudes distributed along the Andes and Yungas in western South America.
With the ancestral species at much lower altitudes, beneficial high altitude alleles could potentially be carried to help in the colonization of neighboring mountain environments. 
Systems of metapopulations like this could potentially arise in many places
where the ancestral species carries around with it beneficial alleles for
 selective pressures it has encountered in the past and remains connected to through hybridization events.

@@

 \paragraph{Atmosphere's ability to carry whoever scotty is beaming up ... }
Perhaps the most notable finding in this study is that large, ancestral populations have the capacity to maintain alleles which are potentially deleterious for an extended amount of time.  
%This system seems analagous the marvel superhero \emph{Rogue}, who can steal superpowers or memories from another  for a limited amount of time as long as she has contact with the indivi
This principle, deriving solely from the properties of sex and natural selection, could be applicable to almost any species experiencing the influence of divergent selection with introgression.
And to explore further how this process is carried out exactly, many of the questions lie in understanding which properties of genomic architecture and demographics allow this transportation to be possible. 
In terms of Star Trek's ``transporter" referred to by \citet{schluter2009genetics}, 
This is largely analogous to exploring the specific properties of the atmosphere / space which allow for the heroes to be disassembled, then put back together.
%While the perspective of our 
In our simulations, the continued gene flow from freshwater populations meant that the alleles were maintained at a constant rate with fixed demographics. 
Two possible questions that might arise from this are:
(1) How do population sizes, demographics, and evolutionary histories impact an ancestral population's capacity for carrying maladaptive alleles in its opposing environment.
(2) What role does genomic architecture play in the ability for a haplotype to be rebuilt

>>>>

In this paper, we have described a realistic simulation model of a coastal metapopulation to observe the effects of selection of genetic variation (SGV) across a wide range of gene flow rates.
We have shown that historical introgression, at our given parameter sets, is able to reproduce rapid and parallel adaptation similar to what we've seen in real populations such as Middleton island. 
Selection is able to rebuild the freshwater haplotype at a rapid pace (in tens of generations) from marine populations as a medium between all freshwater populations. 
Almost all rates of migration were helpful in the efficiency of the population to locally adapt except for the highest at which migration load limited the ability of the populations to reach the local optimum.

While our findings prove useful to the understanding of stickleback, they are not autonomous to this species. 
Now, we will discuss the broader implications of our findings on the more general framework of similar systems, we also explore what other questions remain. 
Small patches of similar selective pressures can be found in many places such as high altitudes, underwater volcanic vents, or post forest fire environments. 
%We are still finding new subspecies, that seem to have adapted to extreme environments presented in small patches connected to larger spanning biospheres where the ancestral species naturally inhabits.
Recently, (Cite Nelson Ferretti et al), discovered seven new species of Hapalotremus (Theraphosinae), living at the extremely high altitudes distributed along the Andes and Yungas in western South America.
With the ancestral species at much lower altitudes, beneficial high altitude alleles could potentially be carried to help in the colonization of neighboring mountain environments. 
Systems of metapopulations like this could potentially arise in many places
where the ancestral species carries around with it beneficial alleles forselective pressures it has encountered in the past and remains connected to through hybridization events.

@@

 \paragraph{Atmosphere's ability to carry whoever scotty is beaming up ... }
Perhaps the most notable finding in this study is that large, ancestral populations have the capacity to maintain alleles which are potentially deleterious for an extended amount of time.  
%This system seems analagous the marvel superhero \emph{Rogue}, who can steal superpowers or memories from another  for a limited amount of time as long as she has contact with the indivi
This principle, deriving solely from the properties of sex and natural selection, could be applicable to almost any species experiencing the influence of divergent selection with introgression.
And to explore further how this process is carried out exactly, many of the questions lie in understanding which properties of genomic architecture and demographics allow this transportation to be possible. 
%In terms of Star Trek's ``transporter" referred to by \citet{schluter2009genetics}, 
his is largely analogous to exploring the specific properties of the atmosphere / space which allow for the heroes to be disassembled, then put back together.
%While the perspective of our 
In our simulations, the continued gene flow from freshwater populations meant that the alleles were maintained at a constant rate with fixed demographics. 
Two possible questions that might arise from this are:
(1) How do population sizes, demographics, and evolutionary histories impact an ancestral population's capacity for carrying maladaptive alleles in its opposing environment, and 
(2) What role does genomic architecture play in the ability for a haplotype to be rebuilt.
